\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-03-20 paper.tex
added corrections

The Joystream protocol attempts to formalize a  content platform which is governed and operated by the platform users. The centerpiece of the protocol is the shared platform state, implemented on top of a blockchain consensus system, which coordinates and incentives all stakeholders. Almost every aspect of a content platform is endogenous to the protocol, including

    \begin{itemize}
        \item[(a)] {governance}
        \item[(b)] {membership system, with screening and policing}
        \item[(c)] {storage and distribution}
        \item[(d)] {curated content directory}
        \item[(e)] {content search, browsing and recommendations}
        \item[(f)] {software development finance and coordination}
        \item[(g)] {content production financing}
        \item[(h)] {advertising auctions and placement}
        \item[(i)] {communication: messaging and message boards}
    \end{itemize}

and every subsystem is fully accountable to, and directed by, the users, as represented by the governance process. Capturing such a broad range of systems in the protocol is \textit{the} distinguishing characteristic of this proposal. It is motivated by the thesis that a high level of platform accountability may be achieved by empowering two user capabilities.

Firstly, the ability to voice discontent, and subsequently implement changes based on such voices. This relies on an immutable history of actions, reliable information sharing, and binding execution of policy changes.

Secondly, the ability to exit the platform at low cost, and create an alternative, when platform decay has gone too far. This relies upon having the entire platform state available for whole sale replication, which is not possible if critical parts of the platform state are exogenous to the protocol.

@@

The goal of this document is to give a high level overview of design approach for of a new protocol for content platforms. This is an evolving document which is meant as a basis for a iterative review, technical specification and testing, and revised versions will be developed on the basis of that process. Multiple aspects of the protocol are still subject to active research, and any part of the current design may be amended or entirely abandoned as a result of subsequent considerations. Lastly, the descriptive resolution varies substantial across the proposal as a result of different parts being at radically different levels of maturity.

@@

Due to a mixture of conspiring factors, such as platform externalities, economies of scale and jurisdictional arbitrage, dominant contemporary internet platforms have become some of the least accountable organizations we have. The traditionally constraining institutions of market competition, regulation and litigation, appear simultaneously unable to push back against their market power. The social cost of this equilibrium is multifaceted, leading to lower innovation, platform rents, and more broadly that platform policy is only incidentally, not primarily, guided by the objectives of the largest platform stakeholder: \textit{users}. Users should be broadly understood to mean anyone who participates on a platform in any capacity.

@@

The Joystream protocol is an attempt at formalizing the structure and function of a content platform where user accountability is a key objective and organizing principle. This accountability is generated by technically codifying two well known complementary responses to organizational decline \cite{hirschman1970exit}.

@@

    Users have effective means of sharing information, coordinating and reaching decisions about key collective action problems, namely how to allocate and regulate use of any shared platform asset.

@@

    Users have effective means of creating new platform instances which preserve the entire platform history and state. This ability to fully replicate the technical, administrative and economic state of a platform has two positive effects on accountability. Firstly, it empowers the voice of users through the threat of a low cost exist. Secondly, it supports the emergence of a diversity of platforms when the underlying interests of stakeholders are irreconcilably incompatible, or where organizational decline as gone sufficiently far.

@@

In order to build in the capacity for such responses, the Joystream protocol is built as follows. Shared platform state lives on an open blockchain consensus system. As a result, it has a public state and history, and which is fully auditable and immutable. The protocol also has secure direct and broadcast communication capabilities integrated with a platform identity system. This means that it is very cheap for any participant to securely inspect the system, and make irrefutable positive claims as part of subsequent public deliberation, learning, debate or agitation. The identity system, along with an immutable history of public actions and communications, generates the incentive to invest in community standing and act with a long time horizon. Further, there is a governance mechanism which allows low cost coordination around how shared assets should be used and regulated, and how the protocol itself should be amended. Importantly this mechanism is self-executing, and thus provides reliable and counterparty free implementation of governance decisions. All of these properties work in concert to support \textit{voice} as response.

The protocol itself is open, is implemented in open source reference software, has open shared state and data accessible for all. This makes the copying step of creating an alternative instantiation trivial, and thus supports \textit{exit} as response.

@@

Occasionally there may be reference to data types in various schemas or concept definitions, assume the C++ type system.

When identifier fields are used in definitions, assume that they are unique, and that the are created by auto-incrementation in the context of some set of existing instances.

Constant values are displayed with capitalized snake case as follows: {\tiny FOO\_BAR}. These are values which cannot be changed through governance, and require a hard fork or consensus upgrade. On some occasions the symbol {\tiny C} will be used to denote some constant which is specific to the context.

@@

The Joystream protocol is stateful, and the infrastructure for the secure distribution and updating of this state is a blockchain system.
A given instantiation of the Joystream protocol runs on its own single purpose blockchain infrastructure, which only processes transactions related to this instantiation. In the rest of the document this blockchain will be treated as a silent transaction ordering mechanism, but in what follows it is briefly described what assumptions are made about the blockchain infrastructure in the protocol design. Here, and in the rest of the document, the \textit{platform or platform state} will refer to the state upon which transactions operate. In Bitcoin, this would for example be the UTXO set. This would be as distinct from the state of the underlying blockchain infrastructure itself, namely the actual chain of blocks designated by the chain selection rule.

@@

The blockchain has a consensus algorithm in the classical BFT algorithm family, adapted to use Proof-of-Stake based voting power for a dynamic validator\footnote{We will refer to a block producing actor as a \textit{validator}, and anyone simply fully validating the chain as a \textit{full validator}.} set. A designated platform token, described further in section \ref{sec:accounts_and_tokens}, is used by the validators to stake, and it is also the unit in which they are rewarded. There is a growing set of such consensus protocols \cite{tendermint, kiayias2017ouroboros, algorand}, and the following general properties of these systems are of importance to the protocol design.

@@

    \item[-] \textbf{High throughput and low latency:} In benchmarks, these algorithms have been shown to support combinations confirmation latency, transaction throughput, validator count and geographic distribution, which are substantially more attractive than that found in typical production Nakamoto consensus chains \cite{cosmos}.

@@

    \item[-] \textbf{Light client friendly:} The overwhelming majority of end users will need to securely access the platform in computing environments with resource constraints, such as browsers and mobile devices. They also should be able to quickly start interacting with the platform, even if the last sign-on was a long time ago, or it may even be the first time. In addition, the Joystream protocol will have a large state and transaction history. These constraints make a light client protocol the only genuine interaction model for almost all users.

    In these algorithms, a light client only needs to track any potential changes in the validator set, which in practice will change quite infrequently, for example due to the unbonding period induced delay, and not in large increments. Once an up to date validator set is identified, the client can securely read any part of the platform state by authenticating merkle proofs from full nodes against state commitments found in the relevant block header.

    Contrast this with Nakamoto consenus systems, where all block headers starting at genesis\footnote{For reference, Ethereum has a chain of more than 7.1M blocks as of Jan. 22 2019.} must initially be downloaded, and one must keep up with new blocks as the system moves forward\footnote{For reference, Ethereum commits 5760 new blocks per day as of Jan. 22 2019.}. Headers are validated and the chain selection rule is applied on a continuous basis. Even if feasible, this requires a long initial synchronization period whenever a client comes on line for the first time, or at some point after a hiatus.

@@

    \item[-] \textbf{Finality:} The finality of block commitment is the property that once two-thirds of the current validator set has signed off on a block, then that block will become, and remain, part of the chain permanently. Contrast this with Nakamoto consenus systems  where the heaviest chain selection rule can in principle fork off any block, albeit with exponentially declining probability in the block depth, from the chain. This property has a number of critical benefits

@@

        In order for secure assertions about the state of the Joystream chain, to be feasible on a different chain, it will effectively need to behave as a light client that can track the most up to date committed block on the Joystream chain. Finality ensures that tracking this becomes very easy, because there are no reorganization events that can occur. Such events open up the possibility of attacking whatever asset ownership, or general state management, changes executed on the remote chain prior to the reorganization. Dealing with this is complex, and will often involve introducing delays. Moreover, the light client friendliness discussed above also helps in reducing how much information must be submitted to the remote chain light client.

@@

        Finality ensures that the incentive to attack a chain in order to perform a double spend through a reorganization goes away. This risk is particularly high in the early stage of the lifetime of a new blockchain, as the amount of work (or stake) initially drawn to the system may be particularly low. Even beyond the launch, the amount of value securing the system will always fluctuate, in particular for nascent systems, and thus finality provides a valuable guarantee.

@@

It is possible to upgrade both the transaction validation rules, and the current state of the chain, through the transaction processing system itself. This is typically enabled by having the transaction validation rules be stored in the state, and run them on top of some virtualization layer. This property is a requirement for the following:

@@

    \item[-] \textbf{Genuine accountability:} Without a formalized mechanism for both measuring the preferences of stakeholders on collective action decisions, and exercising those decisions, there will be an inevitable development of off-chain social conventions and authorities which operate as stuarts and coordinators in such scenarios. Such actors are not accountable to platform stakeholders in any well defined or transparent way, which is undesirable in of itself.

    \item[-] \textbf{Faster iteration:} For the protocol rules to quickly evolve, the process for coordinating around such changes must economize on critical ecosystem resources, such as attention, information processing and legitimacy. Opaque off-chain upgrading processes risk becoming a perpetual source of conflict around questions of legitimacy. Moreover, the requirement for active upgrading of validator software, and the non-committing signaling games which often surround such events, are an additional practical friction. Instead, endogenous upgrading, with an accompanying on-chain immutable record of deliberation, and an history of such updates, can offer an effective remedy against these difficulties.

    \item[-] \textbf{Developer fungibility:} In general, a complex system, where any failure is catastrophic, will tend to constrain the number of developers who securely can contribute to the improvement of the system. This constraint can in the extreme support a kind of market power in the hands of key developers, where they can end up becoming gate keepers for any change to be applied.

    In the context of upgrading blockchain systems, the reliance on off-chain upgrades to the consensus rules, the state transition function must incorporate the full history of rule sets from genesis, to the most recent changes, in order to be able to validate all blocks. In practice this ends up with an monotonically increasing complexity confronting developers wanting to comprehend and modify the system, which is problematic, as explained.

@@

Certain kinds of transactions may occasionally be required which take a long time to process. Specifically, they may even require more time to process than what is feasible when consuming all the the block time across multiple blocks. In some cases it may be possible to accommodate such processing by the following approach, referred to as Asynchronous Transaction Processing (ATP). When the transaction is processed, and is valid, an appropriate subset of the blockchain state is locked, in the sense that all other transaction types which mutate it are considered invalid. In order to implement this in an orderly fashion, where it is practical to reason about what transactions are impacted by a given subset, one should confine the approach to suitable transaction types. Now during this locking period, which typically will last for a predefined number of blocks, the validator nodes are free to conduct the desired processing for the initial transaction outside of the normal sequential validation of blocks, for example on a separate processing unit. The locking prevents any race condition. Finally, when the time has expired, the finalized processing result is committed to the blockchain state at the end of the corresponding block, and the substate locking is no longer in effect.

@@

    \item[-] \textbf{Transactional:}  The normal transactional pay per use model found in the majority of currency focused systems, such as Bitcoin. This mode applies to basic operations, such as moving fund.

    \item[-] \textbf{Block Range Action Quota (BRAQ):} An \textit{action} refers to a combination of an actor, role and transaction type. This model prevents a given action from occurring more than a given number of time over a given number of blocks. Successfully issuing such transactions within the given limits do not involve marginal outlay for the given actor.

@@

Given that BRAQ will cover the majority of transactions, security would be primarily be financed through minting tokens, which also more closely matches the public goods nature of chain security. This dual model has a number of critical benefits for platform.

Firstly, it dramatically reduces the transactions costs of onboarding new users who initially have no tokens and either face prohibitive costs in acquiring, storing and using them, or need to be persuaded about the value of the platform before being willing to incur such costs. Such users will instead face the option of being onboarded via a screening mechanism (see section \ref{sec:membership_curation}). After this they will be able to immediately interact with the system, within constraints. Users may later earn or purchase tokens in order to escape quota limitations. Alternatively, the platform itself may simply eventually abandon the free policy once these costs have declined sufficiently, as a result of general increase in maturity of the blockchain ecosystem.

Secondly, this approach explicitly subjects the fee model to a dynamic governance process, where all default limits, and individual member quotas, can be adjusted. This is an easy, and possible the only feasible, long term mechanism for correcting the externalities associated with long term social cost of transaction processing and state utilization in public chains \cite{blockchain_resource_pricing}.

@@

In the BRAQ model, two parameters are required for each action, the \textit{range length}, denoted by $R$, and the \textit{action quota}, denoted by $Q$, both being positive integers. A combined range length and transaction limit is called a \textit{BRAQ quota}. The model prevents an action in a given block if there are already $L$ such actions in the current to $R$ blocks back. The system must maintain a sequence of positive integers $H=(h_1, \ldots, h_N)$, called the \textit{event list}, for each action, initially set to an empty list. A combined BRAQ quota and such list is called \textit{BRAQ instance}.
An action should not be allowed in block height $h$ when

@@

otherwise it should proceed to normal validation. If the corresponding transaction is subsequently found to be accepted, the new value for $H$ should be

@@

where $M=N$ if $N < L$, otherwise $M = N - 1$. Hence $H$ is a list of block heights for, up to, the last $N$ successful actions. The benefit of the event list is that it makes it easy for a light client to track availability of a given action at any given time, as the entire BRAQ instance is securely available in the state. A full node could in principle track and enforce an instance without having the $H$ in the state.

Lastly, when using this model, it may in some cases be desirable to share the same quota across a range of instances. This is typically if you are dealing with a very large number of instances which all have very similar actors. At the same time, it can also be ideal to retain the flexibility to have explicitly custom quotas for specific actors, based on policy or discretion. These two goals are accommodated by the concept of a \textit{BRAQ quota proxy}. This is either a normal quota, or it is an identifier resolving a normal quota in some context specific pool of quotas, or simply a sentinel to use some other context specific quota.

@@

Some of the assets that are of value to the platform will inevitably not live in the state of the same blockchain. This could for example be state of a DNS mapping which lives on some other system, like ENS \cite{ens} or Handshake \cite{handshake}. It may even be desirable to move certain  assets from the Joystream blockchain, such as tokens, over onto other blockchain systems. While proposals are being developed to support very general inter blockchain transaction routinely, such as Cosmos \cite{cosmos} for tokens and Polkadot \cite{polkadot}, its not clear when or if they will be fully deployed, and to what extent the Joystream blockchain will be able to benefit, or more simply whether the Joystream governance process will converge on such an integration.

A direct and simple case by case integration will be possible by using the same standard technique used in almost all secure blockchain integration proposals. For each blockchain which needs to be integrated with Joystream, deploy a light client instance on each side, for the opposite side, where there is a requirement to write to the state on of the first. This obviously requires that the given side is expressive and economical enough to support such an on-chain light client. So for example, take the case of wanting to subject an ENS mapping, on Ethereum, to the governance processes on the Joystream blockchain. This would only require deploying a Joystream light client contract on Ethereum which also is set as the owner to the given mapping. Block headers comitted to the Joystream blockchain would have to be submitted to this light client, at the very least when there were changes in validator sets. A designated party from the Joystream side could be incentivised to regularly do this. This header history in the state of the contract would allow it to be securely convinced of the ENS related signaling actions on the Joystream side through Merkle proofs, since these would be committed to in the corresponding headers\footnote{This could be in the event logging system, or individual transaction types being included in blocks.}. The contract could then in turn execute the corresponding on chain contract call to put this signal into effect in ENS.

@@

The platform has a standard for account based (fungible) token ownership. There will be a primary token, called the \textit{native token}, which will be part of initial state of the platform. This native token will, as will be described later, be used for value transfer, bonding and governance activities.

New tokens are minted continuously for a very wide range of purpose, all primarily to reward some actor for some behavior. This minting is perpetual, and how much is minted for what purpose is controlled by the platform governance process. New tokens are also burned by actors in scenarios where they need to contribute value to the platform through the token, e.g. purchasing ad placements. There is no platform treasury which would otherwise absorb these tokens. As a result of these three separate exogenous dynamics - and the platform upgradeability functionality, there is no ex-ante certainty about the total supply of the token at different points in time in the future.

The other tokens are related to the content finance market, described further in section \ref{sec:content_finance}. They are issued by publishing a \textit{token profile} into a registry, called the \textit{token registry}. A token profile includes include key information, such as a standard token symbol, issuer identifier, description and also the ownership state itself, called the \textit{token balances}. The token balances simply maps a public key to a positive integer, and a single mapping represents the quantity of tokens under the control of whomever holds the private key which corresponding the public key. The registration of a key in the balances of a token is referred to as an \textit{account}. Reuse of the same key pair across accounts for the same actor is an individual policy choice. Normal spending operations can be conducted from an account to any new, or existing, account on the same token, by being able to sign a message with a private key that matches the public key corresponding to the origin account. The token registry is a mapping from a \textit{token identifier}, which is a unique positive integer, to the corresponding token profile. The native token has identifier $0$.

Notice that the following account model is distinct from the smart contract account model in general, where all transactions are tied to a given account, although such platforms also have an account based token ownership model. Transactions are instead on Joystream, at least most of the time, tied to membership, explained in further detail in section \ref{sec:member}.

@@

% Move later?
The membership concept is meant unify all platform level participation for the same actor in a way which is independent of token ownership in the account system. This means that all platform level actions are with reference to a particular membership. A given member may of course occupy a range of different roles through the same membership, and membership is conceptually a base role in itself. Having an integrated representation of the participation of a single actor is very valuable in supporting efficient communication and collaboration, and it supports pro-social investment in actor reputation. Separating this from token holdings is valuable, as it allows for allowing some types participation to be possible without tokens, for example as a means for actors to earn their first tokens

@@

A \textit{member} is an actor who is registered in the \textit{membership registry}, and is defined as follows \\

@@

\begin{concept_box}{Paid Membership Terms}
    \begin{itemize}
      \item[-] \textbf{ID:} Unique integer identifier, called \textit{term ID}.
      \item[-] \textbf{Fee:} Quantity of native token which must be provably burned.
      \item[-] \textbf{Proxy Quota:} Initial quota for membership.
      \item[-] \textbf{Text:} String of capped length (UTF-8) describing the human readable conditions which are being agreed upon.
    \end{itemize}
\end{concept_box}

>>>>

The Joystream protocol attempts to formalize a content platform that is governed and operated by the platform users. The centerpiece of the protocol is the shared platform state, implemented on top of a blockchain consensus system, which coordinates and provides incentives to all stakeholders. Almost every aspect of a content platform is endogenous to the protocol, including

    \begin{itemize}
        \item[(a)] {governance}
        \item[(b)] {membership system, with screening and policing}
        \item[(c)] {storage and distribution}
        \item[(d)] {curated content directory}
        \item[(e)] {content search, browsing, and recommendations}
        \item[(f)] {software development finance and coordination}
        \item[(g)] {content production financing}
        \item[(h)] {advertising auctions and placement}
        \item[(i)] {communication: messaging and message boards}
    \end{itemize}

and every subsystem is fully accountable to, and directed by, the users, as represented by the governance system. Capturing such a broad range of systems in the protocol is \textit{the} distinguishing characteristic of this proposal. It is motivated by the thesis that a high level of platform accountability can be achieved by empowering two user capabilities.

First, the ability to voice discontent and subsequently implement changes based on such voices, which relies on an immutable history of actions, reliable information sharing, and binding execution of policy changes.

Second, the ability to exit the platform at a low cost and create an alternative when the platform decay has gone too far. This relies on having the entire platform state available for wholesale replication, which is not possible if critical parts of the platform state are exogenous to the protocol.

@@

This document aims to give a high level overview of the design approach for of a new protocol for content platforms. This is an evolving document meant as a basis for an iterative review, technical specification and testing, and revised versions will be developed on the basis of that process. Multiple aspects of the protocol are still subject to active research, and any part of the current design may be amended or entirely abandoned as a result of subsequent considerations. Lastly, the descriptive resolution varies substantially across the proposal as a result of different parts at radically different levels of maturity.

@@

Due to a mixture of conspiring factors, such as platform externalities, economies of scale and, jurisdictional arbitrage, dominant contemporary Internet platforms have become some of the least accountable organizations today. The traditionally constraining institutions of market competition, regulation and litigation simultaneously appear to be unable to push back against their market power. The social cost of this equilibrium is multifaceted, leading to lower innovation, platform rents, and more broadly to the fact that platform policy is only incidentally, not primarily, guided by the objectives of the largest platform stakeholder: \textit{users}. Users should be broadly understood as anyone who is participating on a platform in any capacity.

@@

The Joystream protocol is an attempt at formalizing the structure and function of a content platform, where user accountability is a key objective and organizing principle. This accountability is generated by technically codifying two well-known complementary responses to organizational decline \cite{hirschman1970exit}.

@@

    Users have effective means of sharing information, coordinating, and reaching decisions about key collective action problems, namely how to allocate and regulate the use of any shared platform asset.

@@

    Users have effective means of creating new platform instances that can preserve the entire platform history and state. This ability to fully replicate the technical, administrative, and economic state of a platform has two positive effects on accountability: first, it empowers the voice of users through the threat of a low cost exist; and second, it supports the emergence of a diversity of platforms when the underlying interests of stakeholders are irreconcilably incompatible or where the organizational decline as gone sufficiently far.

@@

In order to build in the capacity for such responses, the Joystream protocol is built as follows. The shared platform state lives on an open blockchain consensus system. As a result, it has a public state and history that is fully auditable and immutable. The protocol also has secure direct and broadcast communication capabilities integrated within a platform identity system. This means that it is very cheap for any participant to securely inspect the system and make irrefutable positive claims as part of subsequent public deliberation, learning, debating, or agitating. The identity system along with an immutable history of public actions and communications generates the incentive to invest in community standing and act with a long time horizon. Further, there is a governance mechanism that allows low cost coordination around the use and regulation of shared assets and the amendment of the protocol. Importantly this mechanism self executes and thus provides reliable and a counterparty-free implementation of governance decisions. All these properties work in hand to support \textit{voice} as response.

The protocol itself is open and implemented in open source reference software. It has an open shared state and data accessible for all. This makes the copying step of creating an alternative instantiation trivial and thus supports \textit{exit} as response.

@@

Occasionally, there may be reference to data types in various schemes or concept definitions, assume the C++ type system.

When identifier fields are used in definitions, assume that they are unique and created by auto-incrementation in the context of some set of existing instances.

Constant values are displayed with a capitalized snake case as follows: {\tiny FOO\_BAR}. These are values that cannot be changed through governance and require a hard fork or consensus upgrade. In some occasions, the symbol {\tiny C} is used to denote some constant that is specific to the context.

@@

The Joystream protocol is stateful, and the infrastructure for the secure distribution and updating of this state is a blockchain system.
A given instantiation of the Joystream protocol runs on its own single-purpose blockchain infrastructure, which only processes transactions related to this instantiation. In the rest of the document, this blockchain will be treated as a silent transaction ordering mechanism; however, in the following section, it will briefly describe the assumptions on the blockchain infrastructure in the protocol design. Here, and in the rest of the document, the \textit{platform or platform state} will refer to the state upon which transactions operate. In Bitcoin, for example, this would be the UTXO set and be distinctive from the state of the underlying blockchain infrastructure itself, namely the actual chain of blocks designated by the chain selection rule.

@@

The blockchain has a consensus algorithm in the classical BFT algorithm family that is adapted to use Proof-of-Stake-based voting power for a dynamic validator\footnote{We will refer to a block producing actor as a \textit{validator}, and anyone simply fully validating the chain a \textit{full validator}.} set. A designated platform token, described further in section \ref{sec:accounts_and_tokens}, is used by the validators to stake and is also the unit in which they are rewarded. There is a growing set of such consensus protocols \cite{tendermint, kiayias2017ouroboros, algorand}, and the following general properties of these systems are of importance to the protocol design.

@@

    \item[-] \textbf{High throughput and low latency:} In benchmarks, these algorithms have been shown to support combinations of confirmation latency, transaction throughput, validator count, and geographic distribution, which are substantially more attractive than that found in typical production Nakamoto consensus chains \cite{cosmos}.

@@

    \item[-] \textbf{Light client friendly:} The overwhelming majority of end users will need to securely access the platform in computing environments with resource constraints, such as browsers and mobile devices. They should also be able to quickly start interacting with the platform, even if the last sign-on was a long time ago or may even be the first time. In addition, the Joystream protocol will have a large state and transaction history. These constraints make a light client protocol the only genuine interaction model for almost all users.

    In these algorithms, a light client only needs to track any potential changes in the validator set, which in practice changes quite infrequently, for example, due to the unbonding period induced delay and not in large increments. Once an up-to-date validator set is identified, the client can securely read any part of the platform state by authenticating merkle proofs from full nodes against state commitments found in the relevant block header.

    This is in contrast to Nakamoto consenus systems where all block headers starting at genesis\footnote{For reference, Ethereum has a chain of more than 7.1M blocks as of Jan. 22 2019.} must initially be downloaded, and one must keep up with new blocks as the system moves forward\footnote{For reference, Ethereum commits 5760 new blocks per day as of Jan. 22 2019.}. Headers are validated, and the chain selection rule is applied on a continuous basis. Even if feasible, this requires a long initial synchronization period whenever a client comes on line for the first time or at some point after a hiatus.

@@

    \item[-] \textbf{Finality:} The finality of block commitment is the property that once two-thirds of the current validator set has signed off on a block, then that block will become, and remain, part of the chain permanently. This is in contrast to Nakamoto consenus systems where the heaviest chain selection rule can in principle fork off any block, albeit with exponentially declining probability in the block depth, from the chain. This property has a number of critical benefits

@@

        In order for secure assertions about the state of the Joystream chain to be feasible on a different chain, this chain will effectively need to behave as a light client that can track the most up-to-date committed block on the Joystream chain. Finality ensures that tracking this becomes very easy, as there are no reorganization events that can occur. Such events open up the possibility of reverting the basis critical state changes executed on the remote chain prior to the reorganization, e.g. changes in asset ownership. Dealing with this is complex and will often involve introducing delays. Moreover, the light client friendliness discussed above also helps in reducing the information to be submitted to the remote chain light client.

@@

        Finality ensures that the incentive to attack a chain to perform a double spend through a reorganization goes away. This risk is particularly high in the early stage of the lifetime of a new blockchain, as the initial amount of work (or stake) on the system may be particularly low. Even beyond the launch, the amount of value securing the system will always fluctuate, in particular for nascent systems;  thus, finality provides a valuable guarantee.

@@

It is possible to upgrade both the transaction validation rules and the current state of the chain through the transaction processing system itself. This can typically be enabled by storing the transaction validation rules in the state and then running them on top of some virtualization layer. This property is a requirement for the following:

@@

    \item[-] \textbf{Genuine accountability:} Without a formalized mechanism for both measuring the preferences of stakeholders on collective action decisions and exercising those decisions, there will be an inevitable development of off-chain social conventions and authorities who will operate as stuarts and coordinators in such scenarios. Such actors are not accountable to platform stakeholders in any well defined or transparent way, which is undesirable in itself.

    \item[-] \textbf{Faster iteration:} For the protocol rules to quickly evolve, the process to coordinate around such changes must economize on critical ecosystem resources, such as attention, information processing, and legitimacy. Opaque off-chain upgrading processes risk becoming a perpetual source of conflict around questions of legitimacy. Moreover, the requirement for active upgrading of validator software and the non-committing signaling games that often surround such events are an additional practical friction. Instead, endogenous upgrading with an accompanying on-chain immutable record of deliberation and a history of such updates can offer an effective remedy against these difficulties.

    \item[-] \textbf{Developer fungibility:} In general, a complex system where any failure is catastrophic will require constraining the number of developers who can securely contribute to the improvement of the system. This constraint can in extreme cases support a market power in the hands of key developers, where they can end up becoming gate keepers for any change to be applied.

    In the context of upgrading blockchain systems, the reliance on off-chain upgrades to the consensus rules, the state transition function must incorporate the full history of rule sets from genesis to the most recent changes to validate all blocks. In practice, this ends up with a monotonically increasing complexity confronting developers wanting to comprehend and modify the system, which is problematic, as explained.

@@

Certain types of transactions that may take a long time to process are occasionally required. Specifically, they may even require more time to process more than what is feasible when consuming all the the block times across multiple blocks. In some cases, it may be possible to accommodate such processing by the following approach, referred to as Asynchronous Transaction Processing (ATP). When the transaction is processed, and is valid, an appropriate subset of the blockchain state is locked in the sense that all other transaction types that mutate it are considered invalid. In order to implement this in an orderly fashion, where it is practical to reason about what transactions are impacted by a given subset, one should confine the approach to suitable transaction types. Now, during this locking period, which typically will last for a predefined number of blocks, the validator nodes are free to conduct the desired processing for the initial transaction outside the normal sequential validation of blocks, for example, on a separate processing unit. The locking prevents any race condition. Finally, when the time has expired, the finalized processing result is committed to the blockchain state at the end of the corresponding block, and the substate locking is no longer in effect.

@@

    \item[-] \textbf{Transactional:}  The normal transactional pay-per-use model can be found in a majority of currency-focused systems such as Bitcoin. This mode applies to basic operations such as moving fund.

    \item[-] \textbf{Block Range Action Quota (BRAQ):} An \textit{action} refers to a combination of an actor, role, and transaction type. This model prevents a given action from occurring more than a given number of time over a given number of blocks. Successfully issuing such transactions within the given limits does not involve marginal outlay for the given actor.

@@

Given that BRAQ will cover the majority of transactions, security will primarily be financed through minting tokens, which also more closely matches the public goods nature of chain security. This dual model has a number of critical benefits for platform.

First, it drastically reduces the transactions costs of onboarding new users who initially have no tokens and either face prohibitive costs in acquiring, storing, and using them or need to be persuaded about the value of the platform before being willing to incur such costs. Such users will instead face the option of being onboarded via a screening mechanism (see section \ref{sec:membership_curation}). After this, they will be able to immediately interact with the system, within constraints. Users may later earn or purchase tokens to escape quota limitations. Alternatively, the platform itself may simply eventually abandon the free policy once these costs have declined sufficiently as a result of general increase in maturity of the blockchain ecosystem.

Second, this approach explicitly subjects the fee model to a dynamic governance process where all default limits and individual member quotas can be adjusted. This is an easy and possibly the only feasible long term mechanism for correcting the externalities associated with the long-term social cost of transaction processing and state utilization in public chains \cite{blockchain_resource_pricing}.

@@

In the BRAQ model, two parameters are required for each action: the \textit{range length}, denoted by $R$, and the \textit{action quota}, denoted by $Q$; both are positive integers. A combined range length and transaction limit is known as a \textit{BRAQ quota}. This model prevents an action in a given block if there are already $L$ such actions in the current $R$ blocks prior. The system must maintain a sequence of positive integers $H=(h_1, \ldots, h_N)$, known as the \textit{event list}, for each action, initially set to an empty list. A combination of BRAQ quota and such a list is referred to as \textit{BRAQ instance}.
An action should not be allowed in block height $h$ when

@@

otherwise it will proceed to normal validation. If the corresponding transaction is subsequently found to be accepted, then the new value for $H$ should be

@@

where $M=N$ if $N < L$, otherwise $M = N - 1$. Hence, $H$ is a list of block heights for, up to, the last $N$ successful actions. The benefit of the event list is that it makes it easy for a light client to track the availability of a given action at any given time, as the entire BRAQ instance is securely available in the state. A full node could in principle track and enforce an instance without having the $H$ in the state.

Lastly, when using this model, it is in some cases desirable to share the same quota across a range of instances. This is typically if you are dealing with a very large number of instances all of which have very similar actors. At the same time, it is also ideal to retain the flexibility to have explicitly custom quotas for specific actors based on policy or discretion. These two goals are accommodated by the concept of a \textit{BRAQ quota proxy}. This is either a normal quota or an identifier resolving a normal quota in some context-specific pool of quotas or simply a sentinel to use some other context specific quota.

@@

Some of the assets that are of value to the platform will inevitably not live in the state of the same blockchain. This can, for example, be the state of a DNS mapping that lives on some other system, such as ENS \cite{ens} or Handshake \cite{handshake}. It may even be desirable to move certain assets from the Joystream blockchain, such as tokens, onto other blockchain systems. While proposals are being developed to support very general inter-blockchain transaction routinely, such as Cosmos \cite{cosmos} for tokens and Polkadot \cite{polkadot}, it is not clear when or if they will be fully deployed, and to what extent the Joystream blockchain will be able to benefit, or more simply whether the Joystream governance process will converge on such an integration.

A direct and simple case-by-case integration will be possible by using the same standard technique in almost all secure blockchain integration proposals. For each blockchain that needs to be integrated with Joystream, deploy a light client instance on each side, for the opposite side, where there is a requirement to write to the state on the first. This obviously requires that the given side is expressive and economical enough to support such an on-chain light client. Take the example of wanting to subject an ENS mapping, on Ethereum, to the governance processes on the Joystream blockchain. This will only require deploying a Joystream light client contract on Ethereum, which also is set as the owner to the given mapping. Block headers committed to the Joystream blockchain will then have to be submitted to this light client, at the very least when there are changes in validator sets. A designated party from the Joystream side can be incentivised to regularly conduct this. This header history in the state of the contract will allow it to be securely convinced of the ENS-related signaling actions on the Joystream side through Merkle proofs, since these will be committed to in the corresponding headers\footnote{This could be in the event logging system, or individual transaction types being included in blocks.}. The contract can then in turn execute the corresponding on-chain contract call to put this signal into effect in ENS.

@@

The platform has a standard for account-based (fungible) token ownership. There will be a primary token, called the \textit{native token}, which will be part of the initial state of the platform. This native token will, as will be described later, be used for value transfer, bonding, and governance activities.

New tokens are minted continuously for a very wide range of purposes, all primarily to reward some actor for some behavior. This minting is perpetual, and how much is minted for what purpose is controlled by the platform governance process. New tokens are also burned by actors in scenarios where they need to contribute to the platform through the token; e.g. purchasing ad placements. There is no platform treasury that will otherwise absorb these tokens. As a result of these three separate exogenous dynamics - and the platform upgradeability functionality, there is no ex-ante certainty about the total supply of the token at different points in time in the future.

The other tokens are related to the content finance market, described further in section \ref{sec:content_finance}. They are issued by publishing a \textit{token profile} into a registry called the \textit{token registry}. A token profile includes key information, such as a standard token symbol, issuer identifier, description, and also the ownership state itself known as the \textit{token balances}. The token balances simply maps a public key to a positive integer, and a single mapping represents the quantity of tokens under the control of whoever holds the private key corresponding to the public key. The registration of a key in the balances of a token is referred to an \textit{account}. Reuse of the same key pair across accounts for the same actor is an individual policy choice. Normal spending operations can be conducted from an account to any new or existing account on the same token by signing a message with a private key that matches the public key corresponding to the original account. The token registry is a mapping from a \textit{token identifier}, which is a unique positive integer, to the corresponding token profile. The native token has identifier $0$.

Note that the following account model is distinct from the smart contract account model in general, where all transactions are tied to a given account, although such platforms also have an account-based token ownership model. Transactions are instead on Joystream, at least most of the time, tied to membership, which has been explained in further detail in section \ref{sec:member}.

@@

% Move later?
The membership concept is meant to unify all platform-level participation for the same actor in a way that is independent of token ownership in the account system. This means that all platform level actions are with reference to a particular membership. A given member may of course occupy a range of different roles through the same membership. Membership is conceptually a base role in itself. Having an integrated representation of the participation of a single actor is very valuable in supporting efficient communication and collaboration and supports pro-social investment in the actor's reputation. Separating this from token holdings is valuable, as it allows for some type of participation to be possible without tokens, for example, as a means for actors to earn their first tokens

@@

A \textit{member} is an actor who is registered in the \textit{membership registry} and is defined as follows: \\

@@

\begin{concept_box}{Paid Membership Terms}
    \begin{itemize}
      \item[-] \textbf{ID:} Unique integer identifier known as \textit{term ID}.
      \item[-] \textbf{Fee:} Quantity of native token that must be provably burned.
      \item[-] \textbf{Proxy Quota:} Initial quota for membership.
      \item[-] \textbf{Text:} String of capped length (UTF-8) describing the human readable conditions to be agreed upon.
    \end{itemize}
\end{concept_box}

The platform has a set of terms, called the \textit{active paid membership terms}, which are currently in place for anyone seeking paid membership. It is updated through a council proposal. Any new terms introduced by the council must have an ID greater than the prior active terms; the initially active terms have an ID of $0$. The full history of such terms that were once active is kept in a list known as the \textit{paid membership terms record}, which maps the term ID to the corresponding terms.
